Network Fusion through CDRP Model\\ Decomposition and Assembly

### 2020-01-10 paper/paper.tex
Update paper.tex
change to booktabs
change to varnothing

\begin{algorithm}[h]
	\caption{The General Algorithm}
	\label{tab:heuristic-search}
	\begin{algorithmic}[1]
		\Require The inputs to the assembly problem;
		\Ensure $D$, a classifier set satisfying constraints, or $\emptyset$ if not feasible.
		\State $Q \gets \emptyset$; \Comment A priority queue, the last element $h$ is the key
		\Function{Expand}{$D$} \Comment $D$, the classifier set
			\For{$d \in \mathcal{D} - D$}
				\State Calculate the encoding $C$ using $D \cup \{d\}$;
				\State Calculate the entropy $h$ for $C$;
				\State $Q \gets Q \cup \{(D \cup \{d\}, C, h)\}$;
			\EndFor
		\EndFunction
		\Function{HeuristicSearch}{}
			\State $\Call{Expand}{\emptyset}$;
			\While{$Q \neq \emptyset$}
				\State $(D, C, h) \gets Pop(Q)$;
				\If{$e_0 == 0$}
					\State \Return $D$;
				\EndIf
				\If{|D| < k}
					\State $\Call{Expand}{D}$;
				\EndIf
			\EndWhile
			\State \Return $\emptyset$;
		\EndFunction
	\end{algorithmic}
\end{algorithm}

@@

\begin{table}[h]
	\caption{Corresponding Class Labels of Each Cluster}
	\label{tab:cluster_label}
	\begin{tabular}{|c|c|c|}
	\hline
	\multirow{2}{*}{Classifier} &\multicolumn{2}{|c|}{Possible Class Labels}\\
	\cline{2-3}
	& In (0) & Not in (1)\\
	\hline
	classifier-0,6 & 4 & 0,1,2,3,4,5\\
	classifier-1 & 1 & 0,2,3,4,5\\
	classifier-2 & 2 & 0,1,3,4,5\\
	classifier-3 & 0 & 1,2,3,4,5\\
	classifier-4 & 3 & 0,1,2,4,5\\
	classifier-7 & 3,4 & 0,1,2,3,4,5\\ 
	classifier-9 & 2,3,4 & 0,1,5\\ 
	classifier-8,13 & 0 & 1,2,3,4,5\\
	classifier-10,12 & 1 & 0,1,2,3,4,5\\
	classifier-11 & 3 & 0,1,2,3,4,5\\
	\hline
	\end{tabular}
\end{table}

@@

    \caption{Accuracy of Chosen Binary-Classifiers}
    \label{tab:classifer-accuracy}
	\begin{tabular}{|c|c|c|c|c|}
	\hline
	Classifier ID & 3 & 4 & 1 & 2 \\
	\hline
	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 62.3\% & 82.3\% & 83.5\% & 67.0\%\\
	\hline
	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
	\hline
	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 97.5\% & 80.5\% & 94.5\% & 89.5\%\\
	\hline
	\end{tabular}
\end{table}

@@

    \caption{Encoding and Accuracy of Each Class Label}
    \label{tab:encoding-and-accuarcy}
	\begin{tabular}{|c|c|c|c|c|c|c|}
	\hline

	Class ID & 0 & 1 & 2 & 3 & 4 & Overall \\
	\hline
	Encoding &0 & 110 & 1110 &10 & 1111 & -\\
	\hline
	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 100\% & 30.0\% & 11.0\% & 28.0\% & 7.0\% & 34.4\%\\

	\hline
	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 92.0\% & 93.0\% & 58.0\% & 85.0\% & 67.0\% & 79.0\%\\
	\hline
	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 95.0\% & 91.0\% & 76.0\% & 78.0\% & 76.0\% & 83.2\%\\

	\hline

>>>>

\begin{algorithm}[h]
	\caption{The General Algorithm}
	\label{tab:heuristic-search}
	\begin{algorithmic}[1]
		\Require The inputs to the assembly problem;
		\Ensure $D$, a classifier set satisfying constraints, or $\varnothing$ if not feasible.
		\State $Q \gets \varnothing$; \Comment A priority queue, the last element $h$ is the key
		\Function{Expand}{$D$} \Comment $D$, the classifier set
			\For{$d \in \mathcal{D} - D$}
				\State Calculate the encoding $C$ using $D \cup \{d\}$;
				\State Calculate the entropy $h$ for $C$;
				\State $Q \gets Q \cup \{(D \cup \{d\}, C, h)\}$;
			\EndFor
		\EndFunction
		\Function{HeuristicSearch}{}
			\State $\Call{Expand}{\varnothing}$;
			\While{$Q \neq \varnothing$}
				\State $(D, C, h) \gets Pop(Q)$;
				\If{$e_0 == 0$}
					\State \Return $D$;
				\EndIf
				\If{|D| < k}
					\State $\Call{Expand}{D}$;
				\EndIf
			\EndWhile
			\State \Return $\varnothing$;
		\EndFunction
	\end{algorithmic}
\end{algorithm}

@@

\begin{table}[h]
	\caption{Corresponding Class Labels of Each Cluster}
	\label{tab:cluster_label}
	\begin{tabular}{|c|c|c|}
	\hline
	\multirow{2}{*}{Classifier} &\multicolumn{2}{c|}{Possible Class Labels}\\
	\cline{2-3}
	& In (0) & Not in (1)\\
	\hline
	classifier-0,6 & 4 & 0,1,2,3,4,5\\
	classifier-1 & 1 & 0,2,3,4,5\\
	classifier-2 & 2 & 0,1,3,4,5\\
	classifier-3 & 0 & 1,2,3,4,5\\
	classifier-4 & 3 & 0,1,2,4,5\\
	classifier-7 & 3,4 & 0,1,2,3,4,5\\ 
	classifier-9 & 2,3,4 & 0,1,5\\ 
	classifier-8,13 & 0 & 1,2,3,4,5\\
	classifier-10,12 & 1 & 0,1,2,3,4,5\\
	classifier-11 & 3 & 0,1,2,3,4,5\\
	\hline
	\end{tabular}
\end{table}

@@

    \caption{Accuracy of Chosen Binary-Classifiers}
    \label{tab:classifer-accuracy}
	\begin{tabular}{ccccc}
	\toprule
	Classifier ID & 3 & 4 & 1 & 2 \\
	\midrule
	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 62.3\% & 82.3\% & 83.5\% & 67.0\%\\
	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 97.5\% & 80.5\% & 94.5\% & 89.5\%\\
	\bottomrule
	\end{tabular}
\end{table}

@@

    \caption{Encoding and Accuracy of Each Class Label}
    \label{tab:encoding-and-accuarcy}
	\begin{tabular}{ccccccc}
	\toprule
	Class ID & 0 & 1 & 2 & 3 & 4 & Overall \\
	\midrule
	Encoding &0 & 110 & 1110 &10 & 1111 & -\\
	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 100\% & 30.0\% & 11.0\% & 28.0\% & 7.0\% & 34.4\%\\

	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 92.0\% & 93.0\% & 58.0\% & 85.0\% & 67.0\% & 79.0\%\\
	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 95.0\% & 91.0\% & 76.0\% & 78.0\% & 76.0\% & 83.2\%\\
	\bottomrule
